---
output: github_document
---

# rand36sf

**Recode and scale the RAND SF-36 Questionnaire**

The `rand36sf` package recodes and scores the eight scales of the RAND SF-36 Health Survey from raw item responses in a data frame. Items are recoded to a 0-100 scale and averaged to create the eight scales: Physical Functioning, Role Limitations due to Physical Health, Role Limitations due to Emotional Problems, Energy/Fatigue, Emotional Well-Being, Social Functioning, Pain, and General Health. This is done as per the [scoring manual](https://www.rand.org/health/surveys/mos/36-item-short-form/scoring.html).

## Installation

You can install the development version of rand36sf from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("maher42/rand36sf")
```

## Example

`score_rand36sf()` expects each row to be one completed questionnaire: any
leading identifier columns (here, an `id` and a `timepoint`), followed by the
36 SF-36 items in standard order. The bundled data has six respondents, each
measured at two timepoints:

```{r format}
library(rand36sf)

data(sf36_example)
head(sf36_example)
```

The first two columns are identifiers and the items begin at column 3, which is
the default for the function's `start_col` argument.

### Scoring the survey

Pass the data to `score_rand36sf()`. It returns your original data frame with
eight new columns — one per scale — each scored on a 0 to 100 scale, where higher
is better:

```{r score}
scored_df <- score_rand36sf(sf36_example)

head(scored_df)
```

